Preprocess

### 2023-11-29 src/metrics.Rmd
Add in age range for preprocess

```{r}
models_format <- c(
    "_cghr10" = "",
    "_" = " & ",
    "chatgpt3" = "ChatGPT-3",
    "chatgpt4" = "ChatGPT-4",
    "insilicova" = "InSilicoVA",
    "interva5" = "InterVA-5"
)
stage_format <- c(
    "is_" = "",
    "recon" = "Reconciliation",
    "agreed" = "Agreement",
    "adj" = "Adjudication"
)
```

@@

# Create stage with counts
stage_remap <- c(
    "All" = paste0("All\nRecords\n(n=", nall, ", 100%)"),
    "Agreed" = paste0("Physician\nAgreed Records\n(n=", nagree, ", ", round(pagree), "%)"),
    "Reconciled" = paste0("Reconciled\n(n=", nrecon, ", ", round(precon), "%)"),
    "Adjudicated" = paste0("Adjudicated\n(n=", nadj, ", ", round(padj), "%)")
)

# Prepare boxplot data
pdata <- out %>%
    select(
        Model,
        `PCCC`,
        `PCCC Agreement`
    ) %>%
    rename(
         All = `PCCC`,
         Agreed = `PCCC Agreement`
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "Stage",
        values_to = "PCCC"
    ) %>%
    mutate( # re-order stage
        Stage = factor(Stage, levels = c(
            "Agreed",
            "All"
        ))
    ) %>%
    mutate( # rename stages with counts
        Stage = recode(Stage, !!!stage_remap)
    ) %>%
    group_by(Stage) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.03, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
    )

# Plot boxplot
pplot <- pdata %>%
    ggplot(aes(x = Stage, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_dotplot(
        binaxis = "y",
        binwidth = 0.03,
        dotsize = 0.3,
        fill = "white",
        color = "darkgray",
        stackdir = "center",
        stackratio = 2,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#3d3d3d",
        size = 2,
        position = position_nudge(y = -0.06, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#3d3d3d",
        size = 2,
        position = position_nudge(y = 0.065, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Mid`),
        color = "#3d3d3d",
        size = 2,
        position = position_nudge(y = -0.065, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    geom_segment(aes(x = -Inf, y = 0, xend = Inf, yend = 0), arrow = arrow(length = unit(1, "cm"))) +
    labs(
        x = element_blank(),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.2, 0.8) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 5)),
        axis.title.y = element_text(margin = margin(r = 5)),
        axis.line.x = element_line(
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        ),
        axis.line.y = element_blank()
    )

# Save the plot
pplot
ggsave("../manuscript/fig-perf-allvsagree.pdf", plot = pplot, dpi = 300)
```

@@

Display a plot of performance for agreed

>>>>

```{r}
models_format <- c(
    "_cghr10" = "",
    "_" = " & ",
    "chatgpt3" = "ChatGPT-3.5",
    "chatgpt4" = "ChatGPT-4",
    "insilicova" = "InSilicoVA",
    "interva5" = "InterVA-5"
)
stage_format <- c(
    "is_" = "",
    "recon" = "Reconciliation",
    "agreed" = "Agreement",
    "adj" = "Adjudication"
)
```

@@

# Create stage with counts
stage_remap <- c(
    "All" = paste0("All\nRecords\n(n=", nall, ", 100%)"),
    "Agreed" = paste0("Physician Agreed\nRecords\n(n=", nagree, ", ", round(pagree), "%)"),
    "Reconciled" = paste0("Reconciled\n(n=", nrecon, ", ", round(precon), "%)"),
    "Adjudicated" = paste0("Adjudicated\n(n=", nadj, ", ", round(padj), "%)")
)

# Prepare boxplot data
alldata <- out %>%
    select(
        Model,
        `PCCC`,
        `PCCC Agreement`
    ) %>%
    rename(
         All = `PCCC`,
         Agreed = `PCCC Agreement`
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "Stage",
        values_to = "PCCC"
    ) %>%
    mutate( # re-order stage
        Stage = factor(Stage, levels = c(
            "Agreed",
            "All"
        ))
    ) %>%
    mutate( # rename stages with counts
        Stage = recode(Stage, !!!stage_remap)
    ) %>%
    group_by(Stage) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.05, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.97, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, "\n(", round(PCCC, 2), ")"), NA),
        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
    )

# Plot boxplot
allplot <- alldata %>%
    ggplot(aes(x = Stage, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_dotplot(
        binaxis = "y",
        binwidth = 0.03,
        dotsize = 0.3,
        fill = "white",
        color = "darkgray",
        stackdir = "center",
        stackratio = 2,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2,
        position = position_nudge(y = 0.065, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Mid`),
        color = "#4d4d4d",
        size = 2,
        position = position_nudge(y = -0.065, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    geom_segment(aes(x = -Inf, y = 0, xend = Inf, yend = 0), arrow = arrow(length = unit(1, "cm"))) +
    labs(
        x = element_blank(),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.2, 0.8) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 5)),
        axis.title.y = element_text(margin = margin(r = 5)),
        axis.line.x = element_line(
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        ),
        axis.line.y = element_blank()
    )

# Save the plot
allplot
ggsave("../manuscript/fig-perf-allvsagree.pdf", plot = allplot, dpi = 300)
```

### COD Performance

Plot model performance for physician agreed records by cause of death category.

```{r}
```

@@

Display a plot of performance for physician agreed records by age group.

# Calc age counts
nagree <- nrow(df %>% filter(is_agreed == TRUE))
nadult <- nrow(df %>% filter(age == "adult" & is_agreed == TRUE))
nchild <- nrow(df %>% filter(age == "child" & is_agreed == TRUE))
nneo <- nrow(df %>% filter(age == "neo" & is_agreed == TRUE))

# Calc age perc
padult <- (nadult / nagree) * 100
pchild <- (nchild / nagree) * 100
pneo <- (nneo / nagree) * 100

# Create age with counts
age_remap <- c(
    "Adult" = paste0("Adult\n12+ years\n(n=", nadult, ", ", round(padult), "%)"),
    "Child" = paste0("Child\n28 days to 11 years\n(n=", nchild, ", ", round(pchild), "%)"),
    "Neonatal" = paste0("Neonatal\n<28 days\n(n=", nneo, ", ", round(pneo), "%)")
)

# Prepare boxplot data
agedata <- out %>%
    select(
        Model,
        `PCCC Adult Agreement`,
        `PCCC Child Agreement`,
        `PCCC Neo Agreement`
    ) %>%
    rename(
         Adult = `PCCC Adult Agreement`,
         Child = `PCCC Child Agreement`,
         Neonatal = `PCCC Neo Agreement`
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "Age Group",
        values_to = "PCCC"
    ) %>%
    mutate( # re-order age
        "Age Group" = factor(`Age Group`, levels = c(
            "Neonatal",
            "Child",
            "Adult"
        ))
    ) %>%
    mutate( # rename ages with counts
        "Age Group" = recode(`Age Group`, !!!age_remap)
    ) %>%
    group_by(`Age Group`) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(PCCC <= min(PCCC) * 1.15, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Max" = if_else(PCCC >= max(PCCC) * 0.95, paste0(Model, " (", round(PCCC, 2), ")"), NA),
        "PCCC Mid" = if_else(is.na(`PCCC Min`) & is.na(`PCCC Max`), paste0(Model, "\n(", round(PCCC, 2), ")"), NA),
        "PCCC Min" = if_else(`PCCC` == min(PCCC), paste(na.omit(`PCCC Min`), collapse = "\n"), NA), # Combine into one row if close PCCC
        "PCCC Max" = if_else(`PCCC` == max(PCCC), paste(na.omit(`PCCC Max`), collapse = "\n"), NA)
    )

# Plot boxplot
ageplot <- agedata %>%
    ggplot(aes(x = `Age Group`, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_dotplot(
        binaxis = "y",
        binwidth = 0.03,
        dotsize = 0.3,
        fill = "white",
        color = "darkgray",
        stackdir = "center",
        stackratio = 2,
        position = position_nudge(x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2,
        position = position_nudge(y = 0.055, x = -0.3)
    ) +
    geom_text(
        aes(label = `PCCC Mid`),
        color = "#4d4d4d",
        size = 2,
        hjust = 1,
        position = position_nudge(y = -0.015, x = -0.3)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.025),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.025),
        size = 3
    ) +
    geom_segment(aes(x = -Inf, y = 0, xend = Inf, yend = 0), arrow = arrow(length = unit(1, "cm"))) +
    labs(
        x = paste0("Agreed Records (n=", nagree, ", 100%)"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.2, 0.8) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.line = element_line(color = "black"),
        axis.title.x = element_text(margin = margin(t = 5)),
        axis.title.y = element_text(margin = margin(r = 5)),
        axis.line.x = element_line(
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        ),
        axis.line.y = element_blank()
    )

# Save the plot
ageplot
ggsave("../manuscript/fig-perf-ages.pdf", plot = ageplot, dpi = 300)
```

### 2023-11-29 src/preprocess.Rmd
Add in age range for preprocess

```{r}
df$physician <- df$physician %>%
    mutate(
        physician_icd10 = coalesce(
            adj_icd,
            p1_recon_icd,
            p1_icd
        ),
        is_agreed = if_else(
            is.na(p1_recon_icd) & is.na(p2_recon_icd) & is.na(adj_icd),
            TRUE,
            FALSE
        ),
        is_recon = if_else(
            !is.na(p1_recon_icd) | !is.na(p2_recon_icd),
            TRUE,
            FALSE
        ),
        is_adj = if_else(
            !is.na(adj_icd),
            TRUE,
            FALSE
        )
    ) %>%
    select(
        rowid,
        round,
        age,
        p1_icd,
        p2_icd,
        p1_recon_icd,
        p2_recon_icd,
        adj_icd,
        is_agreed,
        is_recon,
        is_adj,
        physician_icd10
    )
head(df$physician)
```

>>>>

```{r}
df$physician <- df$physician %>%
    mutate(
        physician_icd10 = coalesce(
            adj_icd,
            p1_recon_icd,
            p1_icd
        ),
        is_agreed = if_else(
            is.na(p1_recon_icd) & is.na(p2_recon_icd) & is.na(adj_icd),
            TRUE,
            FALSE
        ),
        is_recon = if_else(
            !is.na(p1_recon_icd) | !is.na(p2_recon_icd),
            TRUE,
            FALSE
        ),
        is_adj = if_else(
            !is.na(adj_icd),
            TRUE,
            FALSE
        )
    ) %>%
    select(
        rowid,
        round,
        age,
        age_range,
        p1_icd,
        p2_icd,
        p1_recon_icd,
        p2_recon_icd,
        adj_icd,
        is_agreed,
        is_recon,
        is_adj,
        physician_icd10
    )
head(df$physician)
```
